Sound Similarity, Sound Matching, and Differentiable Audio Synthesizer Control

### 2025-04-24 main.tex
Updates from Overleaf

\documentclass[lettersize,journal]{IEEEtran}% \documentclass[twocolumn,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{stfloats} % for positioning of figure* on the same page
\usepackage{caption}
\usepackage{tikz}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage[breaklinks=true,colorlinks=true, allcolors=blue]{hyperref}
\usepackage{breakcites}
\usepackage{microtype}
\usepackage{lipsum}
\usepackage{xcolor}
\usepackage{array}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{csquotes}
\usepackage{makecell}
\usepackage{pdfpages}

\usetikzlibrary{positioning,shapes.geometric}
\usepackage[acronym,toc]{glossaries}

% \input{glossary.tex}

% Initialize the glossary
\makeglossaries

\definecolor{highlight}{RGB}{00,150,00}
\definecolor{todo}{RGB}{200,50,00}
\definecolor{rank1}{HTML}{70FF70}
\definecolor{rank2}{HTML}{858585}
\definecolor{rank3}{HTML}{454545}
\definecolor{rank4}{HTML}{000000}

@@

\newcommand{\BPNoise}{\textbf{BP-Noise}}  
\newcommand{\AddSineSaw}{\textbf{Additive-SineSaw}}  
\newcommand{\AmpMod}{\textbf{Noise-AM}}  
\newcommand{\FMMod}{\textbf{SineSaw-AM}}

\input{code_style}

\title{Sound Similarity, Sound Matching, and Differentiable Audio Synthesizer Control}
\author{ }

@@

\printglossary
\clearpage

\maketitle
\begin{abstract}
Manual sound design with a synthesizer is an iterative process. When an artist has a target sound in mind, they listen to the output of their chosen synthesizer, determine whether the output is closer or farther from the target, and adjust the synthesizer's parameters until satisfied. There are practically an infinite number of parameter combinations, and their effect on the output sound is hard to predict. Iterative sound-matching is the automation of this process, more formally, the automatic programming of an audio synthesizer to generate outputs similar to a target sound while guided by a loss function that quantifies sound similarity.
Past works in sound-matching often relied on a narrow range of synthesizers and overlooked the possible interactions between the loss function and synthesis parameters.
% There are critical choices which need to be made in sound-matching: these are the choice of synthesizer, algorithms for search and optimization, the source of sounds, and similarity (or loss) functions.  We categorize sound-matching works based on these choices, and point out a number of unresolved issues and interesting yet unexplored areas. 
We analyzed the interplay between four simple subtractive, additive, and FM synthesizers when guided by four different novel or established similarity functions.
For each loss function and synthesizer pair, we ran 300 experiments with randomized initial values and targets, and used the final parameter configurations and spectrogram distances as key performance evaluation metrics of the performance. A post-hoc analysis of these performance measures showed that the best‐performing loss function varies based on the method of synthesis at hand, which highlights the value of novel similarity measures and de-prioritizes the search for the elusive universally optimal sound similarity measure.
\end{abstract}

%  Like other problems in computing science, there appears to be an ever present drive towards finding optimal solutions to the problem, and outperforming state-of-the-art.

\section{Introduction}
\subsection{Digital Synthesis With Sound-Matching}
Since the 1970s, artists such as Suzanne Ciani~\cite{ciani_life_in_waves} have explored the use of audio synthesizers to replicate natural sounds---such as a bottle cap popping off---in a way that preserves the essential qualities of the original while showcasing the characteristics of the synthesizer. This approach goes beyond mere replication and uses synthesizers for artistic re-interpretation of sounds. Inspired by this, we aim to emulate and automate this process using digital audio synthesizers.

@@

Esling \textit{et al.} also noted the issue of using P-Loss in sound-matching~\cite{esling2019flow}, considering the non-linear mapping between parameters of a synth and the audio output. In their approach, dubbed as \textquote{flowsynth}, they used a large parameter-to-audio dataset for a commercial \gls{VST} synthesizer. In flowsynth, audio is encoded to an auditory space, using a NN autoencoding approach~\cite{hinton2006reducing}. The encodings in the auditory space can then be converted to the parameter space, but only for that particular synthesizer. Using P-Loss and Spectral Convergence (Frobenius norm of the spectrograms) as metrics, flowsynth outperformed other NN approaches that did not use an auditory to parameter space conversion, but formal hearing tests were not conducted.

@@

A general overview of the programs and the predefined parameter ranges is given in Table~\ref{tab:programs}. In the following subsections, we describe the programs and their parameters in more detail, followed by the methodology in Section~\ref{sec:methodology} and results in Section~\ref{sec:results_posthoc}.
\begin{table*}[htbp]
\centering
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|l|}
\hline
\textbf{ID} & \textbf{Parameters} & \makecell{\textbf{Param. 1}\\\textbf{Range}} & \makecell{\textbf{Param. 2}\\\textbf{Range}} & \textbf{Description} \\
\hline
\BPNoise & hp\_cut, lp\_cut & 50-1000 & 1-120 & Band-pass of Noise signal \\
\hline
\AddSineSaw & saw\_freq, sine\_freq & 20-1000 & 20-1000 & Addition of sine and saw waves \\
\hline
\AmpMod & amp, carrier & 1-20 & 20-1000 & LFO on amplitude of noise osc \\
\hline
\FMMod & amp, carrier & 0-5 & 0-4 & LFO on amplitude of saw osc \\
\hline
\end{tabular}
\end{adjustbox}
\caption{Overview of Program Parameters and the range of values each parameter can take.}
\label{tab:programs}
\end{table*}

\subsubsection{\BPNoise}
\label{sec:program0}
\begin{lstlisting}[caption={\BPNoise}, label={lst:program0},language=Faust,float,floatplacement=htbp,xleftmargin=2em,xrightmargin=1em,firstnumber=0]
import("stdfaust.lib");
lp_cut = hslider("lp_cut",900,50,1000,1);
hp_cut = hslider("hp_cut",100,1,120,1);
process = no.noise:fi.lowpass(3,lp_cut):fi.highpass(10,hp_cut);
\end{lstlisting}

\BPNoise{} is a bare bones example of subtractive synthesis using digital filters~\cite{smith2007introduction}. Despite the ubiquity of subtractive synthesis in practical sound design, it has rarely been tested in differentiable sound-matching. In this program, a noise signal is fed through a band-pass (BP) filter. This removes the frequencies outside the low-pass (LP) and high-pass (HP) cutoffs. The noise generator produces all frequencies with random variation over time. The LP filter removes frequencies over its threshold frequency, and the HP removes frequencies lower than its threshold~\cite{smith2007introduction}. The search parameters are the cutoff thresholds for the LP and HP filters. Listing~\ref{lst:program0} shows the Faust code for \BPNoise.

\subsubsection{\AddSineSaw}
\label{sec:program1}

\begin{lstlisting}[caption={\AddSineSaw}, label={lst:program1},language=Faust,float,floatplacement=TBH,xleftmargin=2em,xrightmargin=1em,firstnumber=0]
import("stdfaust.lib");
saw_freq = hslider("saw_freq",800,20,1000,1);
sine_freq = hslider("sine_freq",300,20,1000,1);
sineOsc(f) = +(f/ma.SR) ~ ma.frac:*(2*ma.PI) : sin;
sawOsc(f) = +(f/ma.SR) ~ ma.frac;
process = sineOsc(sine_freq)+sawOsc(saw_freq);
\end{lstlisting}

@@

\subsubsection{\AmpMod}
\label{sec:program2}
\begin{lstlisting}[caption={\AmpMod}, label={lst:program2},language=Faust,float,floatplacement=TBH,xleftmargin=2em,xrightmargin=1em,firstnumber=0]
import("stdfaust.lib");
amp = hslider("amp",0.5,0,5,0.01);
modulator = hslider("modulator",0.5,0,4,0.01);
sineOsc(f) = +(f/ma.SR) ~ ma.frac:*(2*ma.PI) : sin;
process = no.noise*sineOsc(modulator)*amp;
\end{lstlisting}

@@

\label{sec:program3}
\begin{lstlisting}[caption={\FMMod}, label={lst:program3},language=Faust,float,floatplacement=TBH,xleftmargin=2em,xrightmargin=1em,firstnumber=0]
import("stdfaust.lib");
carrier = hslider("carrier",100,20,1000,1);
amp = hslider("amp",6,1,20,1);
sineOsc(f) = +(f/ma.SR) ~ ma.frac:*(2*ma.PI) : sin;
sawOsc(f) = +(f/ma.SR) ~ ma.frac;
process = sineOsc(amp)*sawOsc(carrier);
\end{lstlisting}
Relative to additive and subtractive synthesis, AM/FM synthesis are less common methods of sound design. Due to their frequent use in previous works, we also tested an AM synthesizer. The synthesizer program is the multiplication of a low frequency sine oscillator with frequency parameter \textit{amp}, and a saw oscillator with frequency parameter \textit{carrier}. Listing~\ref{lst:program3} is the Faust code for \FMMod.

@@

\subsubsection{\BPNoise}
For this synthesizer program, the spectrogram-based models performed the best. This makes intuitive sense, as the visual effects of a band-pass filter on white noise are readily apparent in a spectrogram. As shown in Figure~\ref{fig:npsk_p0}, manual hearing test and MSS selected \SIMSESpec~as the best performer and \LoneSpec~as the second-best performer, while P-loss gave the reverse order. 
\begin{figure}[htbp]
    % \centering
 \begin{minipage}{0.045\textwidth}
    \footnotesize
    \raggedleft
    \vspace{-0.4 cm} SIMSE\\[0.25 cm]
    L1\\[0.26 cm]
    JTFS\\[0.26 cm]
    DTW
\end{minipage}%
\begin{minipage}{\textwidth}
    \centering
    \subfloat[Likert Scores]{
        \includegraphics[width=0.3\textwidth]{images/npsk_likert_0.png}
        \label{fig:p0_hearing}
    }\hspace{-0.425cm}  % Reduce space between figures
    \subfloat[Inverse P-Loss]{
        \includegraphics[width=0.3\textwidth]{images/npsk_P-Loss_0.png}
        \label{fig:p0_P-Loss}
    }\hspace{-0.5cm}  % Reduce space between figures
    \subfloat[Inverse MSS]{
        \includegraphics[width=0.3\textwidth]{images/npsk_MSS_0.png}
        \label{fig:p0_MSS}
    }
\end{minipage}
    \caption{\BPNoise~bootstrapped distributions and ranks given by NPSK. Ranks and their corresponding colors from best to worst are \colorbox{rank1}{\textcolor{black}{\textbf{1}}} \colorbox{rank2}{\textcolor{white}{\textbf{2}}} \colorbox{rank3}{\textcolor{white}{\textbf{3}}} \colorbox{rank4}{\textcolor{black}{\textcolor{white}{\textbf{4}}}}
}

    \label{fig:npsk_p0}
\end{figure}

\subsubsection{\AddSineSaw}
As shown in Figure~\ref{fig:npsk_p1}, JTFS was the best performing loss function in all evaluation methods. Moreover, all evaluation methods produced identical results. 
\begin{figure}[htbp]
    % \centering
 \begin{minipage}{0.045\textwidth}
    \footnotesize
    \raggedleft
    \vspace{-0.4 cm} SIMSE\\[0.25 cm]
    L1\\[0.26 cm]
    JTFS\\[0.26 cm]
    DTW
\end{minipage}%
\begin{minipage}{\textwidth}
    \centering
    \subfloat[Likert Scores]{
        \includegraphics[width=0.3\textwidth]{images/npsk_likert_1.png}
        \label{fig:p1_hearing}
    }\hspace{-0.425cm}  % Reduce space between figures
    \subfloat[Inverse P-Loss]{
        \includegraphics[width=0.3\textwidth]{images/npsk_P-Loss_1.png}
        \label{fig:p1_P-Loss}
    }\hspace{-0.5cm}  % Reduce space between figures
    \subfloat[Inverse MSS]{
        \includegraphics[width=0.3\textwidth]{images/npsk_MSS_1.png}
        \label{fig:p1_MSS}
    }
\end{minipage}
    \caption{\AddSineSaw~bootstrapped distributions and ranks given by NPSK. 
}
    \label{fig:npsk_p1}
\end{figure}

\subsubsection{\AmpMod}
IP-Loss and manual hearing tests yield identical rankings, and MSS results vary for for ranks 2 to 4.  It is not surprising that MSS results differ from the hearing tests, as we saw in Table~\ref{tab:kruskal_auto}, MSS showed no significant differences between groups. As shown in Figure~\ref{fig:npsk_p2}, all models selected \DTWEnv~as the best performer. This may be due to \DTWEnv's focus on periodic changes in loudness.
\begin{figure}[H]
    % \centering
 \begin{minipage}{0.045\textwidth}
    \footnotesize
    \raggedleft
    \vspace{-0.4 cm} SIMSE\\[0.25 cm]
    L1\\[0.26 cm]
    JTFS\\[0.26 cm]
    DTW
\end{minipage}%
\begin{minipage}{\textwidth}
    \centering
    \subfloat[Likert Scores]{
        \includegraphics[width=0.3\textwidth]{images/npsk_likert_2.png}
        \label{fig:p2_hearing}
    }\hspace{-0.425cm}  % Reduce space between figures
    \subfloat[Inverse P-Loss]{
        \includegraphics[width=0.3\textwidth]{images/npsk_P-Loss_2.png}
        \label{fig:p2_P-Loss}
    }\hspace{-0.5cm}  % Reduce space between figures
    \subfloat[Inverse MSS]{
        \includegraphics[width=0.3\textwidth]{images/npsk_MSS_2.png}
        \label{fig:p2_MSS}
    }
\end{minipage}
    \caption{\AmpMod~bootstrapped distributions and ranks given by NPSK. 
}
    \label{fig:npsk_p2}
\end{figure}

@@

\begin{figure}[H]
    % \centering
 \begin{minipage}{0.045\textwidth}
    \footnotesize
    \raggedleft
    \vspace{-0.4 cm} SIMSE\\[0.25 cm]
    L1\\[0.26 cm]
    JTFS\\[0.26 cm]
    DTW
\end{minipage}%
\begin{minipage}{\textwidth}
    \centering
    \subfloat[Likert Scores]{
        \includegraphics[width=0.3\textwidth]{images/npsk_likert_3.png}
        \label{fig:p3_hearing}
    }\hspace{-0.425cm}  % Reduce space between figures
    \subfloat[Inverse P-Loss]{
        \includegraphics[width=0.3\textwidth]{images/npsk_P-Loss_3.png}
        \label{fig:p3_P-Loss}
    }\hspace{-0.5cm}  % Reduce space between figures
    \subfloat[Inverse MSS]{
        \includegraphics[width=0.3\textwidth]{images/npsk_MSS_3.png}
        \label{fig:p3_MSS}
    }
\end{minipage}
    \caption{\FMMod~bootstrapped distributions and ranks given by NPSK. 
}
    \label{fig:npsk_p3}
\end{figure}

@@

\clearpage
\bibliographystyle{alpha}
\bibliography{references}

% Include the appendix from the separate file
\include{appendix}
\end{document}

>>>>

\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{csquotes}
\usepackage{makecell}
% my added packages and commands =======================
\usepackage[numbers]{natbib} %removed cite package
\usepackage{tikz}
\usepackage{adjustbox}
\usepackage{listings}

\usepackage{caption}               % re-enable caption functionality
\captionsetup[lstlisting]{justification=centering, singlelinecheck=false}

\usetikzlibrary{positioning,shapes.geometric}

\providecommand{\gls}[1]{#1}
\definecolor{highlight}{RGB}{00,150,00}
\definecolor{todo}{RGB}{200,50,00}
\definecolor{rank1}{HTML}{70FF70}
\definecolor{rank2}{HTML}{858585}
\definecolor{rank3}{HTML}{454545}
\definecolor{rank4}{HTML}{000000}

@@

\newcommand{\BPNoise}{\textbf{BP-Noise}}  
\newcommand{\AddSineSaw}{\textbf{Add-SineSaw}}  
\newcommand{\AmpMod}{\textbf{Noise-AM}}  
\newcommand{\FMMod}{\textbf{SineSaw-AM}}

\input{code_style}
%  ================================

@@

\title{Sound Similarity, Sound Matching, and Differentiable Audio Synthesizer Control}

\author{-}
\maketitle

\begin{abstract}
Manual sound design with a synthesizer is an iterative process. When an artist has a target sound in mind, they listen to the output of their chosen synthesizer, determine whether the output is closer or farther from the target, and adjust the synthesizer's parameters until satisfied. There are practically an infinite number of parameter combinations, and their effect on the output sound is hard to predict. Iterative sound-matching is the automation of this process, more formally, the automatic programming of an audio synthesizer to generate outputs similar to a target sound while guided by a loss function that quantifies sound similarity.
Past works in sound-matching often relied on a narrow range of synthesizers and overlooked the possible interactions between the loss function and synthesis parameters.
We analyzed the interplay between four simple subtractive, additive, and FM synthesizers when guided by four different novel or established similarity functions.
For each loss function and synthesizer pair, we ran 300 experiments with randomized initial values and targets, and used the final parameter configurations and spectrogram distances as key performance evaluation metrics of the performance. A post-hoc analysis of these performance measures showed that the best‐performing loss function varies based on the method of synthesis at hand, which highlights the value of novel similarity measures and de-prioritizes the search for the elusive universally optimal sound similarity measure.
\end{abstract}

\begin{IEEEkeywords}
Machine Learning, Signal Processing, Sound-Matching
\end{IEEEkeywords}

\section{Introduction}
\subsection{Digital Synthesis With Sound-Matching}
Since the 1970s, artists such as Suzanne Ciani~\cite{ciani_life_in_waves} have explored the use of audio synthesizers to replicate natural sounds—such as a bottle cap popping off—in a way that preserves the essential qualities of the original while showcasing the characteristics of the synthesizer. This approach goes beyond mere replication and uses synthesizers for artistic re-interpretation of sounds. Inspired by this, we aim to emulate and automate this process using digital audio synthesizers.

@@

Esling \textit{et al.} also noted the issue of using P-Loss in sound-matching~\cite{esling2019flow}, considering the non-linear mapping between parameters of a synth and the audio output. In their approach, dubbed as ``flowsynth'', they used a large parameter-to-audio dataset for a commercial \gls{VST} synthesizer. In flowsynth, audio is encoded to an auditory space, using a NN autoencoding approach~\cite{hinton2006reducing}. The encodings in the auditory space can then be converted to the parameter space, but only for that particular synthesizer. Using P-Loss and Spectral Convergence (Frobenius norm of the spectrograms) as metrics, flowsynth outperformed other NN approaches that did not use an auditory to parameter space conversion, but formal hearing tests were not conducted.

@@

A general overview of the programs and the predefined parameter ranges is given in Table~\ref{tab:programs}. In the following subsections, we describe the programs and their parameters in more detail, followed by the methodology in Section~\ref{sec:methodology} and results in Section~\ref{sec:results_posthoc}.

\begin{table*}[htbp]
\centering
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|l|}
\hline
\textbf{ID} & \textbf{Parameters} & \makecell{\textbf{Param. 1}\\\textbf{Range}} & \makecell{\textbf{Param. 2}\\\textbf{Range}} & \textbf{Description} \\
\hline
\BPNoise & hp\_cut, lp\_cut & 50-1000 & 1-120 & Band-pass of Noise signal \\
\hline
\AddSineSaw & saw\_freq, sine\_freq & 20-1000 & 20-1000 & Addition of sine and saw waves \\
\hline
\AmpMod & amp, carrier & 1-20 & 20-1000 & LFO on amplitude of noise osc \\
\hline
\FMMod & amp, carrier & 0-5 & 0-4 & LFO on amplitude of saw osc \\
\hline
\end{tabular}
\end{adjustbox}
\caption{Overview of Program Parameters and the range of values each parameter can take.}
\label{tab:programs}
\end{table*}

\subsubsection{\BPNoise}
\label{sec:program0}

\begin{lstlisting}[caption={\BPNoise}, label={lst:program0}, language=Faust,
                  float, floatplacement=htbp, xleftmargin=1em, xrightmargin=0.5em, firstnumber=0]
import("stdfaust.lib");
lp_cut = hslider("lp_cut",900,50,1000,1);
hp_cut = hslider("hp_cut",100,1,120,1);
process = no.noise:fi.lowpass(3,lp_cut):fi.highpass(10,hp_cut);
\end{lstlisting}

\BPNoise{} is a bare bones example of subtractive synthesis using digital filters~\cite{smith2007introduction}. Despite the ubiquity of subtractive synthesis in practical sound design, it has rarely been tested in differentiable sound-matching. In this program, a noise signal is fed through a band-pass (BP) filter. This removes the frequencies outside the low-pass (LP) and high-pass (HP) cutoffs. The noise generator produces all frequencies with random variation over time. The LP filter removes frequencies over its threshold frequency, and the HP removes frequencies lower than its threshold~\cite{smith2007introduction}. The search parameters are the cutoff thresholds for the LP and HP filters. Listing~\ref{lst:program0} shows the Faust code for \BPNoise.
\subsubsection{\AddSineSaw}
\label{sec:program1}

\begin{lstlisting}[caption={\AddSineSaw}, label={lst:program1},language=Faust,float,floatplacement=TBH,xleftmargin=1em,xrightmargin=0.5em,firstnumber=0]
import("stdfaust.lib");
saw_freq = hslider("saw_freq",800,20,1000,1);
sine_freq = hslider("sine_freq",300,20,1000,1);
sineOsc(f) = +(f/ma.SR) ~ ma.frac:*(2*ma.PI) : sin;
sawOsc(f) = +(f/ma.SR) ~ ma.frac;
process = sineOsc(sine_freq)+sawOsc(saw_freq);
\end{lstlisting}

@@

\subsubsection{\AmpMod}
\label{sec:program2}
\begin{lstlisting}[caption={\AmpMod}, label={lst:program2},language=Faust,float,floatplacement=TBH,xleftmargin=1em,xrightmargin=0.5em,firstnumber=0]
import("stdfaust.lib");
amp = hslider("amp",0.5,0,5,0.01);
modulator = hslider("modulator",0.5,0,4,0.01);
sineOsc(f) = +(f/ma.SR) ~ ma.frac:*(2*ma.PI) : sin;
process = no.noise*sineOsc(modulator)*amp;
\end{lstlisting}

@@

\label{sec:program3}
\begin{lstlisting}[caption={\FMMod}, label={lst:program3},language=Faust,float,floatplacement=TBH,xleftmargin=1em,xrightmargin=0.5em,firstnumber=0]
import("stdfaust.lib");
carrier = hslider("carrier",100,20,1000,1);
amp = hslider("amp",6,1,20,1);
sineOsc(f) = +(f/ma.SR) ~ ma.frac:*(2*ma.PI) : sin;
sawOsc(f) = +(f/ma.SR) ~ ma.frac;
process = sineOsc(amp)*sawOsc(carrier);
\end{lstlisting}
Relative to additive and subtractive synthesis, AM/FM synthesis are less common methods of sound design. Due to their frequent use in previous works, we also tested an AM synthesizer. The synthesizer program is the multiplication of a low frequency sine oscillator with frequency parameter \textit{amp}, and a saw oscillator with frequency parameter \textit{carrier}. Listing~\ref{lst:program3} is the Faust code for \FMMod.

@@

\subsubsection{\BPNoise}
For this synthesizer program, the spectrogram-based models performed the best. This makes intuitive sense, as the visual effects of a band-pass filter on white noise are readily apparent in a spectrogram. As shown in Figure~\ref{fig:npsk_p0}, manual hearing test and MSS selected \SIMSESpec~as the best performer and \LoneSpec~as the second-best performer, while P-loss gave the reverse order.

\begin{figure*}[htbp]
    \centering
    \begin{minipage}{0.03\textwidth}
        \footnotesize
        \raggedleft
        \vspace{-.2cm}
        SIMSE\\[0.6cm]
        L1\\[0.65cm]
        JTFS\\[0.65cm]
        DTW
    \end{minipage}%
    \begin{minipage}{0.95\textwidth}
        \centering
        \subfloat[Likert Scores]{
            \includegraphics[width=0.3\textwidth]{images/npsk_likert_0.png}
            \label{fig:p0_hearing}
        }\hspace{0.005\textwidth} % Reduced space between figures
        \subfloat[Inverse P-Loss]{
            \includegraphics[width=0.3\textwidth]{images/npsk_P-Loss_0.png}
            \label{fig:p0_P-Loss}
        }\hspace{0.005\textwidth} % Reduced space between figures
        \subfloat[Inverse MSS]{
            \includegraphics[width=0.3\textwidth]{images/npsk_MSS_0.png}
            \label{fig:p0_MSS}
        }
    \end{minipage}
    \vspace{-0.5em}
    \caption{\BPNoise~bootstrapped distributions and ranks given by NPSK. Ranks and their corresponding colors from best to worst are \colorbox{rank1}{\textcolor{black}{\textbf{1}}}, \colorbox{rank2}{\textcolor{white}{\textbf{2}}}, \colorbox{rank3}{\textcolor{white}{\textbf{3}}}, \colorbox{rank4}{\textcolor{white}{\textbf{4}}}.}
    \label{fig:npsk_p0}
\end{figure*}
\begin{figure*}[htbp]
    \centering
    \begin{minipage}{0.03\textwidth}
        \footnotesize
        \raggedleft
        \vspace{-.2cm}
        SIMSE\\[0.6cm]
        L1\\[0.65cm]
        JTFS\\[0.65cm]
        DTW
    \end{minipage}%
    \begin{minipage}{0.95\textwidth}
        \centering
        \subfloat[Likert Scores]{
            \includegraphics[width=0.3\textwidth]{images/npsk_likert_1.png}
            \label{fig:p1_hearing}
        }\hspace{0.005\textwidth} % Reduced space between figures
        \subfloat[Inverse P-Loss]{
            \includegraphics[width=0.3\textwidth]{images/npsk_P-Loss_1.png}
            \label{fig:p1_P-Loss}
        }\hspace{0.005\textwidth} % Reduced space between figures
        \subfloat[Inverse MSS]{
            \includegraphics[width=0.3\textwidth]{images/npsk_MSS_1.png}
            \label{fig:p1_MSS}
        }
    \end{minipage}
    \vspace{-0.5em}
    \caption{\AddSineSaw~bootstrapped distributions and ranks given by NPSK.}
    \label{fig:npsk_p1}
\end{figure*}
\begin{figure*}[htbp]
    \centering
    \begin{minipage}{0.03\textwidth}
        \footnotesize
        \raggedleft
        \vspace{-.2cm}
        SIMSE\\[0.6cm]
        L1\\[0.65cm]
        JTFS\\[0.65cm]
        DTW
    \end{minipage}%
    \begin{minipage}{0.95\textwidth}
        \centering
        \subfloat[Likert Scores]{
            \includegraphics[width=0.3\textwidth]{images/npsk_likert_2.png}
            \label{fig:p2_hearing}
        }\hspace{0.005\textwidth} % Reduced space between figures
        \subfloat[Inverse P-Loss]{
            \includegraphics[width=0.3\textwidth]{images/npsk_P-Loss_2.png}
            \label{fig:p2_P-Loss}
        }\hspace{0.005\textwidth} % Reduced space between figures
        \subfloat[Inverse MSS]{
            \includegraphics[width=0.3\textwidth]{images/npsk_MSS_2.png}
            \label{fig:p2_MSS}
        }
    \end{minipage}
    \vspace{-0.5em}
    \caption{\AmpMod~bootstrapped distributions and ranks given by NPSK.}
    \label{fig:npsk_p2}
\end{figure*}
\begin{figure*}[htbp]
    \centering
    \begin{minipage}{0.03\textwidth}
        \footnotesize
        \raggedleft
        \vspace{-.2cm}
        SIMSE\\[0.6cm]
        L1\\[0.65cm]
        JTFS\\[0.65cm]
        DTW
    \end{minipage}%
    \begin{minipage}{0.95\textwidth}
        \centering
        \subfloat[Likert Scores]{
            \includegraphics[width=0.3\textwidth]{images/npsk_likert_3.png}
            \label{fig:p3_hearing}
        }\hspace{0.005\textwidth} % Reduced space between figures
        \subfloat[Inverse P-Loss]{
            \includegraphics[width=0.3\textwidth]{images/npsk_P-Loss_3.png}
            \label{fig:p3_P-Loss}
        }\hspace{0.005\textwidth} % Reduced space between figures
        \subfloat[Inverse MSS]{
            \includegraphics[width=0.3\textwidth]{images/npsk_MSS_3.png}
            \label{fig:p3_MSS}
        }
    \end{minipage}
    \vspace{-0.5em}
    \caption{\FMMod~bootstrapped distributions and ranks given by NPSK.}
    \label{fig:npsk_p3}
\end{figure*}

\subsubsection{\AddSineSaw}
As shown in Figure~\ref{fig:npsk_p1}, JTFS was the best performing loss function in all evaluation methods. Moreover, all evaluation methods produced identical results.

\subsubsection{\AmpMod}
IP-Loss and manual hearing tests yield identical rankings, and MSS results vary for for ranks 2 to 4.  It is not surprising that MSS results differ from the hearing tests, as we saw in Table~\ref{tab:kruskal_auto}, MSS showed no significant differences between groups. As shown in Figure~\ref{fig:npsk_p2}, all models selected \DTWEnv~as the best performer. This may be due to \DTWEnv's focus on periodic changes in loudness.

@@

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}
